Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-02-21 paper-webserver.tex
START: edits

No account creation is required to use the platform. A sharable token is automatically created for users upon opening the website, and is embedded into the website address. Users can share results by copying the URL, and files submitted from different computers using the same token will have the results visible to anyone with the same URL.

@@

Future work will focus on adding additional analyses modules to aid genotype to phenotype predictions, and supporting different species. We're currently working on an approach using support vector machines to predict \textit{E.coli} phenotypes \url{https://github.com/superphy/kmer} which will be integrated into Spfy. While the integrated approach of storing and retrieving results provides enormous benefits, the developed analyses modules are self-contained and can easily be integrated into existing platforms such as Galaxy \cite{goecks2010galaxy}, and IRIDA. Spfy's codebase is provided at \url{https://github.com/superphy/backend} and a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.

>>>>

No account creation is required to use the platform. A sharable token is automatically created for users upon opening the website, and is embedded into the website address. Users can share results by copying the URL, and files submitted from different computers using the same token will be visible to anyone with the same URL.

@@

Future work will focus on adding additional analyses modules to aid genotype to phenotype predictions, and supporting different species. We're currently working on an approach using support vector machines to predict \textit{E.coli} phenotypes \url{https://github.com/superphy/kmer} which will be integrated into Spfy. While the integrated approach of storing and retrieving results provides enormous benefits, the developed analyses modules are self-contained and can easily be integrated into existing platforms such as Galaxy, and IRIDA. Spfy's code hosted at \url{https://github.com/superphy/backend}, and is available for free under the open-source Apache 2.0 license; a developer guide is provided at \url{https://superphy.readthedocs.io/en/latest/}.
